---
title: "PP-Plots"
author: "Gener Aviles-R, based on a blog previously published by [John M Quick](http://rtutorialseries.blogspot.in/2009/12/r-tutorial-series-graphic-analysis-of.html?utm_source=feedburner&utm_medium=feed&utm_campaign=Feed:+RTutorialSeries+(R+Tutorial+Series))."
output: html_notebook
---

PP-Plots are a graphic representation of the probability calculated and probability observed in a dataset. Mostly used when evaluating  model performance.
In this excercise a PP-Plot will be used in the process of evaluating a linear model from [enrollment at the University of New Mexico](http://rtutorialseries.blogspot.in/2009/11/r-tutorial-series-simple-linear.html).

###Reading the dataset and creating a model based on enrollment (`ENROLL`) and unemployment (`UNEM`) data.
```{r Reading table and creating lm}
dataset <- read.csv("D:/Dropbox/MsC UABC/2o Semestre/Clases/Estadistica/tareas/datasets/enrollmentNewMexico.csv")
#constructing linear model

lmVar <- lm(ROLL~UNEM, dataset)

```

###Obtaining values for the **lm** model.

```{r}
unstandPred <- predict(lmVar)
unstandResid <- resid(lmVar)

```

The values obtained with the previous lines of code are not standardized, which means that their range is way to different between these vairables, a **standardization** process will solve this problem and allow us to run analysis smoothly on them.

The following formula can be used to standardize a set of values:
$$Z = \frac{x-\mu}{\sigma}$$
Where $x$ is the value being standardized, $\mu$ is the mean of the variable to which the value belongs to and $\sigma$ is the standard deviation of the variable to which the value belongs to.

```{r, message=FALSE, warning=FALSE}
standPred <- (unstandPred - mean(unstandPred)) / sd(unstandPred)
standResid <- (unstandResid - mean(unstandResid)) / sd(unstandResid)
```
###Calculating the probability distribution for residuals

```{r}
probDist <- pnorm(standResid)
plot(ppoints(length(standResid)), sort(probDist), main = "PP Plot", xlab = "Observed Probability", ylab = "Expected Probability")
abline(0,1)
```

###This all can be done with the `ppplot.das` from the `CircStats` package:

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(StatDA)
library(CircStats)
#ppplot.das(dataset$ROLL, pdist = pnorm, xlab = "Enrollment", ylab = "Probability Calculated", line = TRUE)

ppplot.das(standResid, pdist = pnorm, xlab = "Expected Probabilty", ylab = "Observed Probability", line = TRUE)
```

```{r}
pop<-c(20,23,24,24,24,25,29,31,31,33,34,36,36,37,39,39,40,40,41,45)
```