---
title: "Datos de Ricardo"
output:
  html_notebook: default
  pdf_document: default
---

##Raw data

Loading a `.txt` with spaces and no header provided by Ricardo and shwoing the first 6 entries.
```{r}
library(readr)
ric <- read.table("D:/Dropbox/MsC UABC/2o Semestre/Clases/Estadistica/tareas/datasets/ricardocomp.txt", header = FALSE, sep = " ")
head(ric)
```


There are some things that need to be done with this raw dataset:

  - Add Headers to V2, V4 and V9.
  - Eliminate the others, once the first step is done, the rest is not needed.

The 6 first entries of the tidy dataset looks like this:
```{r}
colnames(ric) <- c("V1","V2", "Imagen","V4","V5","Umbral","V7","V8","V9","Cantidad de Ceros")
ric <- ric[,-c(1,2,4,5,7:9), drop = FALSE]
head(ric)
```

For Ricardo and Ernesto it is important to analyze the graph generated with `Umbral` and `Cantidad de Ceros`:
```{r}
plot(ric)
```

```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(ggplot2)
ggplot(ric, aes(x = ric$Umbral, y = ric$`Cantidad de Ceros`)) +
  geom_path(color = ric$Imagen, lineend = "round", show.legend = TRUE) +
  labs(title = "Experimento 3", x = "Valores de Umbral", y = "Cantidad de Información")
```


```{r, message=FALSE, warning=FALSE}
library(readr)
ric2 <- read_csv("D:/Dropbox/MsC UABC/2o Semestre/Clases/Estadistica/tareas/datasets/ricardo2.csv", 
    col_names = FALSE)
View(ric2)


```
Es por esto que pruebo las citas [@sakia1992box], y luego otra cita, esperando que funcionen asi nadamas [@box1964analysis].